Sequential algorithms to split and merge ultra-high resolution 3D images

### 2017-07-29 paper.tex
Minor updates following Yongping's edits

\begin{figure}[h]
  \centering
  \includegraphics[width=0.45\columnwidth]{figures/benchmark-mreads/mreads-comparision-ssd.pdf}
  \hfill
  \includegraphics[width=0.45\columnwidth]{figures/benchmark-mreads/mreads-comparision-hdd.pdf}\\
  \includegraphics[width=0.45\columnwidth]{figures/benchmark-mreads/mreads-breakdown-ssd.pdf}
  \hfill
    \includegraphics[width=0.45\columnwidth]{figures/benchmark-mreads/mreads-breakdown-hdd.pdf}
  \caption{Comparison between Multiple reads, blocks and slices. Left column: SSD. Right column: HDD. Top row: overall merging time. Bottom row: breakdown by read, write and seek time.}
  % Gnuplot file: scripts/blocks-slices/createboxplot.gnplt
\label{fig:multiple-reads}
\end{figure}

@@

\subsubsection{Multiple writes}
\begin{figure}[h]
  \centering
  \includegraphics[width=0.45\columnwidth]{figures/benchmark-mwrites/mwrites-comparision-ssd.pdf}
  \hfill
  \includegraphics[width=0.45\columnwidth]{figures/benchmark-mwrites/mwrites-comparision-hdd.pdf}\\
  \includegraphics[width=0.45\columnwidth]{figures/benchmark-mwrites/mwrites-breakdown-ssd.pdf}
  \hfill
    \includegraphics[width=0.45\columnwidth]{figures/benchmark-mwrites/mwrites-breakdown-hdd.pdf}
  \caption{Comparison between Multiple writes, blocks and slices. Left column: SSD. Right column: HDD. Top row: overall merging time. Bottom row: breakdown by read, write and seek time.}
  % Gnuplot file: scripts/blocks-slices/createboxplot.gnplt
\label{fig:multiple-writes}
\end{figure}

>>>>

\begin{figure}[h]
  \centering
  \includegraphics[width=0.45\columnwidth]{figures/benchmark-mreads/mreads-breakdown-ssd.pdf}
  \hfill
    \includegraphics[width=0.45\columnwidth]{figures/benchmark-mreads/mreads-breakdown-hdd.pdf}
  \caption{Comparison between Multiple reads, blocks and slices. Left: SSD. Right: HDD.}
  % Gnuplot file: scripts/blocks-slices/createboxplot.gnplt
\label{fig:multiple-reads}
\end{figure}

@@

\subsubsection{Multiple writes}
\begin{figure}[h]
  \centering
  \includegraphics[width=0.45\columnwidth]{figures/benchmark-mwrites/mwrites-breakdown-ssd.pdf}
  \hfill
    \includegraphics[width=0.45\columnwidth]{figures/benchmark-mwrites/mwrites-breakdown-hdd.pdf}
  \caption{Comparison between Multiple writes, blocks and slices. Left: SSD. Right: HDD.}
  % Gnuplot file: scripts/blocks-slices/createboxplot.gnplt
\label{fig:multiple-writes}
\end{figure}
